nmds-plots

### 2023-02-20 workflow/notebooks/nmds-plots.Rmd
created updated figures for alpha and beta diversity

---
title: "nmds-plots"
author: "Megan Coden"
date: "2023-02-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("vegan")
# install.packages("readr")
library(vegan)
library(readr)
library(tidyverse)
library(ggplot2)
library(data.table)
library(here)
```

@@

```{r plotnmds, echo=FALSE}
data.scores = as.data.frame(idsa)
idsa_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + geom_point(aes(color = idsa))
data.scores = as.data.frame(attrib)
attrib_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + geom_point(aes(color = attrib))
data.scores = as.data.frame(allcause)
allcause_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + geom_point(aes(color = allcause))

idsa_plot
attrib_plot
allcause_plot

>>>>

---
title: "nmds-plots"
author: "Megan Coden"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("vegan")
# install.packages("readr")
library(vegan)
library(readr)
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(data.table)
library(here)
```

@@

```{r plotnmds, echo=FALSE}
data.scores = as.data.frame(idsa)
idsa_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + geom_point(aes(color = idsa)) + ggtitle("idsa") + theme_bw() + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank(), plot.title = element_text(hjust = 0.5, size = 10)) + scale_color_brewer(palette="Set1")
data.scores = as.data.frame(attrib)
attrib_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + geom_point(aes(color = attrib)) + ggtitle("attrib") + theme_bw() + theme(legend.position = "none", axis.title.x = element_blank(), axis.title.y = element_blank(), plot.title = element_text(hjust = 0.5, size = 10)) + scale_color_brewer(palette="Set1")
data.scores = as.data.frame(allcause)
allcause_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + geom_point(aes(color = allcause)) + ggtitle("allcause") + theme_bw() + scale_color_brewer(palette="Set1", name="is_severe")

allcause_plot <- ggplot(data.scores, aes(x = axis1, y = axis2)) + 
  geom_point(aes(color = allcause)) + 
  ggtitle("allcause") + 
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, size = 10), axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_color_brewer(palette="Set1", name="is_severe")

ggarrange(idsa_plot, attrib_plot, allcause_plot, nrow = 1, widths = c(6, 6, 9))
